In this chapter, we consider the problem of obtaining tight upper and lower bounds
on the Asymptotic Price of Guillotinability (APoG).
See \cref{sec:intro:guill-thin} to recall the definition and significance of APoG.
See \cref{sec:intro:guill-bp} to recall the definition of guillotinable packing
and $k$-stage packing.

We focus on the special case where the items are
$(\delta_W, \delta_H)$-thin rectangles, i.e., each item has
width at most $\delta_W$ or height at most $\delta_H$,
where $\delta_W$ and $\delta_H$ are constants.
We give lower and upper bounds of roughly $4/3$ when
$\delta_W$ and $\delta_H$ are very small constants.

\section{Overview of the Chapter}

In \cref{sec:apog-lb}, we show a lower bound of $4/3$ on APoG
for thin rectangles. Formally, we prove the following theorem.

\begin{restatable}[Hard instance]{definition}{rdefHardItems}
Let $m$ and $k$ be positive integers and $\eps \in (0, 1)$.
Define $\hardItems(m, k, \eps)$ as a set of $4mk$ rectangular items,
where $2mk$ items have width $(1+\eps)/2$ and height $(1-\eps)/2k$,
and $2mk$ items have height $(1+\eps)/2$ and width $(1-\eps)/2k$.
\end{restatable}

\begin{restatable}{theorem}{rthmAPoGLB}
\label{thm:apog-lb}
Let $I \defeq \hardItems(m, k, \eps)$. Let $\opt(I)$ be the number of bins in the
optimal packing of $I$ and $\opt_g(I)$ be the number of bins in the
optimal guillotinable packing of $I$. Then
\[ \frac{\opt_g(I)}{\opt(I)} \ge \frac{4}{3} (1-\eps). \]
This holds true even if items in $I$ are allowed to be rotated.
\end{restatable}

In \cref{sec:thin-gpack}, we give an algorithm for non-rotational 2D GBP,
called $\thinGPack_{\eps}$, that takes a parameter $\eps \in (0, 1)$ as input.
For a set $I$ of $(\delta_W, \delta_H)$-thin rectangles, we show that when
$\delta_W$, $\delta_H$ and $\eps$ are close to 0, $\thinGPack_{\eps}(I)$ outputs a
guillotinable packing of $I$ into roughly $4\opt(I)/3 + O(1)$ bins.
This proves an upper bound of roughly $4/3$ on APoG for thin rectangles.
Formally, we prove the following theorems about $\thinGPack$.

\begin{restatable}{theorem}{rthmThinGPackProps}
\label{thm:thin-gpack-props}
$\thinGPack_{\eps}(I)$ outputs a 4-stage packing of $I$ in time
$O((1/\eps)^{O(1/\eps)} + n\log n)$.
\end{restatable}

\begin{restatable}{theorem}{rthmThinGPackAppx}
\label{thm:thin-gpack-appx}
Let $I$ be a set of items where each item has width at most $\delta_W$
or height at most $\delta_H$. Then $\thinGPack_{\eps}(I)$ uses less than
$\alpha(1+\eps)\opt(I) + 2\beta$ bins, where
\begin{align*}
\Delta &\defeq \frac{1}{2}\left(\frac{\delta_H}{1-\delta_H}
    + \frac{\delta_W}{1-\delta_W}\right)
\\ \alpha &\defeq \frac{4}{3}(1+4\Delta) + 4\eps\left(1 + \frac{7\Delta}{3}\right)
    \le \frac{4}{3}(1+4\Delta)(1+3\eps)
\\ \beta &\defeq \frac{2\Delta(1+\eps)}{\eps^2} + \frac{10}{3}
    + \frac{19\Delta}{3} + \frac{16\Delta\eps}{3}
\end{align*}
\end{restatable}

In \cref{sec:guill-rot}, we show that the APoG for the rotational case
is at most the APoG for the non-rotational case.
So, when are items are thin, we get an upper bound of $4/3$ on APoG
in the rotational case too.
