\prefacesection{Acknowledgements}

I am very grateful to my advisor, Prof.~Arindam Khan,
for how much he has cared for my academic development.
His guidance on many aspects of my life as a student and researcher has been very valuable.
Talking to him has been a great source of motivation and enlightenment for me,
and he has been a pillar of support during my tough times.

I am thankful to my parents, for always encouraging my pursuits of knowledge
and seconding my decision to pursue graduate studies.
Most of my time as a student at IISc has been spent at home in their company
(because of the Coronavirus pandemic) and they have been very helpful
at ensuring that I get a suitable environment for study and research.

I'm grateful to the Indian Institute of Science (IISc)
and its Computer Science and Automation (CSA) department
for its wonderful M.Tech.~Research programme,
which has been a gateway to research for me.

I'm grateful to Prof.~Siddharth Barman, for giving me helpful suggestions
at crucial stages of my life at IISc.
I'm grateful to Prof.~Arindam Khan, Prof.~Anand Louis, Prof.~Chiranjib Bhattacharyya,
Prof.~Arpita Patra, and Prof.~Sanjit Chatterjee for teaching courses at CSA
that I really enjoyed and learned a lot from.
I thank all the other professors at CSA who I got to meet and learn from.

Finally, I'm thankful to all my friends at IISc for the memorable time I spent with them
at the IISc campus (and remotely afterwards, because of the Coronavirus pandemic).
K.V.N. Sreenivas, in addition to being a good friend,
has been a very good research partner and coauthor.
Rameesh Paul has been a great source of intellectual stimulation,
especially during our collaborations on course projects.
I'm grateful for the many interesting academic (and non-academic) discussions with
my friends Swati Allabadi, Arka Ray, Janaky Murthy and many others.
