\chapter{Conclusion and Future Directions}
\label{chap:conclusion}

In this thesis, we studied approximation algorithms for different kinds of
geometric packing problems.

In \cref{chap:gvbp,chap:gv-rbbp}, we give approximation algorithms for the
generalized multidimensional bin packing problem, a problem that has
wide practical applications but had not yet received attention from the
theoretical computer science community.
We hope that our work will drive interest into this problem.
Possible future directions of research for this problem include
obtaining algorithms with better asymptotic approximation ratios,
and identifying important special cases that can be solved efficiently.

In \cref{sec:rna}, we extended the Round-and-Approx framework~\cite{rna,bansal2014binpacking}
to a larger class of bin packing algorithms.
We expect that our progress will help in better understanding the power of
Round-and-Approx and enable the design of better approximation algorithms
for other packing problems.
It would also be interesting to see applications of Round-and-Approx to other
set-cover type problems, like round-SAP and round-UFP~\cite{ElbassioniGGKNP12}.

In \cref{chap:hdhk}, we give approximation algorithms for the rotational version
of geometric bin packing. Our algorithm for 3D GBP
obtains the best-known asymptotic approximation ratio.
Most previous works make assumptions about bin sizes which are unlikely
to hold in practice. Our algorithms, however, don't rely on such assumptions.
An important problem is to obtain better asymptotic approximation
ratios for $d$D GBP, especially 3D GBP.
There is currently an exponential gap between the lower and upper bounds
on the AAR achievable for $d$D GBP (constant lower bound, upper bound of $1.691^{d-1}$).
It would be interesting to reduce this huge gap.

We have seen that for 2D GBP, the algorithm of Bansal, Lodi and Sviridenko~\cite{bansal2005tale}
has an AAR equal to the asymptotic price of guillotinability (APoG).
It is known that $4/3 \le \APoG \le T_{\infty} \approx 1.69103$.
If we could obtain a better upper bound on APoG, that could
give us the best-known algorithm for 2D GBP.
Hence, obtaining tight bounds on APoG is an important problem.
In \cref{chap:guill-thin}, we show that for the special case of $\delta$-\thin{}
rectangles, when $\delta$ is close to 0, both the lower and upper bounds
on APoG are close to $4/3$.
We hope that our work will shed more light on the general case of the problem.
A good next step would be to obtain tight bounds on APoG
when all rectangles are non-$\delta$-\thin{},
and after that focus on the general case of the problem.

In \cref{chap:thin-bp}, we gave an approximation algorithm for 2D GBP
when the rectangles are $\delta$-\thin{}.
Our work indicates that to improve the AAR for 2D GBP,
a good next step would be to focus on the special case of non-$\delta$-\thin{} rectangles.

Finally, it would be interesting to see if our work can be extended to
other problems similar to bin packing, like bin covering~\cite{assmann1984dual} and scheduling.
Another direction is to explore different problem paradigms, like online algorithms,
or different analysis paradigms, like average-case analysis.
