% TITLE PAGE ===================================================================

\newcommand*{\mytitle}{Approximation Algorithms for Geometric Packing Problems}
\newcommand*{\myname}{Eklavya Sharma}
\title{\mytitle}

\submitdate{\monthyeardate\today}
%\mtech
%\phd
\mtechresearch
%\degree{Master of Technology}
\dept{Computer Science and Automation}
\faculty{Faculty of Engineering}
\author{\myname}

% Using the watermark package which is in StyleFiles/
% and to remove DRAFT COPY ONLY appearing on the top of all pages comment out below line
%\watermark{DRAFT COPY ONLY}

\maketitle

\pagenumbering{alph}

% DECLARATION OF ORIGINALITY ===================================================

\begin{center}
\LARGE{\underline{\textbf{Declaration of Originality}}}
\end{center}
\noindent I, \textbf{Eklavya Sharma}, with SR No.~\textbf{04-04-00-10-22-19-1-16644}
hereby declare that the material presented in the thesis titled
\begin{center}
\textbf{\mytitle}
\end{center}
\noindent represents original work carried out by me in the
\textbf{Department of Computer Science and Automation}
at \textbf{Indian Institute of Science}
during the years \textbf{2019-2021}.

\noindent With my signature, I certify that:
\begin{itemize}
\item I have not manipulated any of the data or results.
\item I have not committed any plagiarism of intellectual property.
    I have clearly indicated and referenced the contributions of others.
\item I have explicitly acknowledged all collaborative research and discussions.
\item I have understood that any false claim will result in severe disciplinary action.
\item I have understood that the work may be screened for any form of academic misconduct.
\end{itemize}

\vspace{20mm}
\noindent {\footnotesize{Date: \hfill Student Signature}} \qquad
\vspace{20mm}

\noindent In my capacity as supervisor of the above-mentioned work, I certify
that the above statements are true to the best of my knowledge, and
I have carried out due diligence to ensure the originality of the report.

\vspace{20mm}

\noindent  {\footnotesize{Advisor Name: Arindam Khan\hfill Advisor Signature}} \qquad

% COPYRIGHT ====================================================================

\blankpage

\vspace*{\fill}
\begin{center}
\large\bf \textcopyright \ \myname\\
\large\bf \monthyeardate\today\\
\large\bf All rights reserved
\end{center}
\vspace*{\fill}
\thispagestyle{empty}

% DECLARATION ==================================================================

%\blankpage
%\includepdf[pages={1}]{declaration.pdf}

%\vspace*{\fill}
%\begin{tabular}{p{0.4\columnwidth}p{0.5\columnwidth}}
% {\em Signature of the Author}: & \dotfill \\
% & Your Name \\
% & Dept.\ of Computer Science and Automation \\
% & Indian Institute of Science, Bangalore \vspace{1in}\\
% {\em Signature of the Thesis Supervisor}: & \dotfill \\
% & Your Advisor's Name \\
% & Professor \\
% & Dept.\ of Computer Science and Automation \\
% & Indian Institute of Science, Bangalore
%\end{tabular}
%\vspace*{\fill}
%\thispagestyle{empty}

%\blankpage

% ACKNOWLEDGEMENTS =============================================================

\frontmatter
\input{acknow.tex}

% ABSTRACT =====================================================================

\prefacesection{Abstract}
\input{abstract}

% PUBS on this Thesis ==========================================================

%\prefacesection{Publications based on this Thesis}

\let\oldbibname\bibname
\renewcommand{\bibname}{Publications based on this Thesis}

\begin{thebibliography}{1}

\bibitem{manual-skewedbp}
Arindam Khan and Eklavya Sharma.
\newblock {Tight Approximation Algorithms For Geometric Bin Packing with Skewed
  Items}.
\newblock In {\em APPROX}, volume 207, pages 22:1--22:23, 2021.
\newblock \href {https://doi.org/10.4230/LIPIcs.APPROX/RANDOM.2021.22}
  {\path{doi:10.4230/LIPIcs.APPROX/RANDOM.2021.22}}.

\bibitem{manual-hdhk}
Eklavya Sharma.
\newblock {Harmonic Algorithms for Packing {$d$}-Dimensional Cuboids into Bins}.
\newblock In {\em FSTTCS}, volume 213, pages 32:1--32:22, 2021.
\newblock \href {https://doi.org/10.4230/LIPIcs.FSTTCS.2021.32}
  {\path{doi:10.4230/LIPIcs.FSTTCS.2021.32}}.

\bibitem{manual-gvbp}
Arindam Khan, Eklavya Sharma, and K.~V.~N. Sreenivas.
\newblock Geometry meets vectors: Approximation algorithms for multidimensional
  packing, 2021.
\newblock \href {http://arxiv.org/abs/2106.13951} {\path{arXiv:2106.13951}}.

\end{thebibliography}

\renewcommand{\bibname}{\oldbibname}
