\chapter{Related Problems and Prior Work}
\label{chap:prior-work}

\section{Classical Bin Packing}

In the online version of bin packing, the items arrive one-by-one,
and for each item, we have to immediately and irrevocably pack it into a bin.
In the online version, the (asymptotic) approximation ratio is also called the
(asymptotic) \emph{competitiveness ratio}.
(The non-online version is called the offline version, i.e., where we can read the
whole input before we start packing.)

The Next-Fit algorithm~\cite{johnson-thesis} is one of the simplest algorithms
for the online classical bin packing problem.
In this algorithm, we start with an empty bin, and designate it as the \emph{open bin}.
We repeatedly pack items into the open bin till we
come across an item that doesn't fit in the open bin.
We then \emph{close} that bin and \emph{open} a new bin and resume.
Let $s(I)$ denote the sum of sizes of all items in $I$.
It is easy to prove that Next-Fit uses at most $\ceil{2s(I)}$ bins.
Since $s(I) \le \opt(I)$, we get that Next-Fit is 2-approximate.

Lee and Lee~\cite{leelee} gave an algorithm for online classical bin packing,
called the $\operatorname{Harmonic}_k$ algorithm.
This algorithm takes as input a set $I$ of items and an integer parameter $k \ge 2$.
The number of bins used by $\operatorname{Harmonic}_k$ to pack $I$ is less than
$T_k\opt(I) + k$, where $T_k$ is a decreasing function of $k$
and $T_{\infty} \defeq \lim_{k \to \infty} T_k \approx 1.6910302$.

Many other algorithms have been devised for the online classical bin packing problem.
See \cref{table:online-1bp} for examples and~\cite{handbook-of-combinopt-bp} for a detailed survey.
The best algorithm we are aware of is the Advanced Harmonic algorithm by
Balogh, B\'ek\'esi, D\'osa, Epstein and Levin~\cite{balogh2018}
that has an AAR of 1.57829.

\begin{table}[ht]
\centering
\caption{Online algorithms for classical bin packing.}
\begin{tabular}{ll}
\toprule Algorithm & Approximation guarantee
\\ \midrule Next-Fit~\cite{johnson-thesis}
    & $\le 2\opt(I)$
\\[\defaultaddspace] First-Fit~\cite{dosa2013first}
    & $\le \floor{1.7\opt(I)}$
%\\[\defaultaddspace] \hline Harmonic$_k$~\cite{leelee}
    %& $< T_k\opt(I) + k - H(k-1)$
\\[\defaultaddspace] Harmonic$_k$~\cite{leelee}
    & $< T_k\opt(I) + k$\quad $(T_\infty \approx 1.69103)$
\\[\defaultaddspace] Advanced Harmonic~\cite{balogh2018}
    & $\le 1.57829\opt(I) + O(1)$
\\ \bottomrule
\end{tabular}
\label{table:online-1bp}
\end{table}

Balogh, B\'ek\'esi and Galambos gave a lower bound of $248/161 \approx 1.54037$
on the asymptotic competitive ratio~\cite{balogh2012new}.
This bound was recently improved to 1.54278~\cite{balogh2021new},
which is the best-known lower bound we are aware of.
See~\cite{handbook-of-combinopt-bp} for a detailed survey on lower bounds.

For the offline version of classical bin packing,
First-Fit Decreasing (FFD) is a popular algorithm.
Johnson~\cite{johnson-thesis} showed that the number of bins used by
FFD is at most $(11/9)\opt(I) + 4$.
The additive constant $4$ was improved by D\'osa
to $2/3$, which is tight~\cite{dosa2007tight}.

Lueker and Vega gave the first APTAS for classical bin packing~\cite{bp-aptas}.
This was later improved upon by Karmarkar and Karp to an algorithm
that uses at most $\opt(I) + O(\log^2\opt(I))$ bins~\cite{karmarkar-karp}.
Rothvoss gave an algorithm that uses at most
$\opt(I) + O(\log\opt(I)\log\log\opt(I))$ bins~\cite{rothvoss2013}.
Hoberg and Rothvoss gave an algorithm that uses at most
$\opt(I) + O(\log\opt(I))$ bins~\cite{HobergR17}
(see \cref{table:offline-1bp}).

\begin{table}[ht]
\centering
\caption{Offline algorithms for classical bin packing.}
\begin{tabular}{ll}
\toprule Algorithm & Approximation guarantee
\\ \midrule First-Fit Decreasing (FFD)~\cite{dosa2007tight}
    & $\le \frac{11}{9}\opt(I) + \frac{2}{3}$
\\[\defaultaddspace] Lueker, Vega~\cite{bp-aptas}
    & $\le (1+\eps)\opt(I) + O(1/\eps^2)$
\\[\defaultaddspace] Karmarkar, Karp~\cite{karmarkar-karp}
    & $\le \opt(I) + O(\log^2\opt(I))$
\\[\defaultaddspace] Rothvoss~\cite{rothvoss2013}
    & $\le \opt(I) + O(\log\opt(I)\log\log\opt(I))$
\\[\defaultaddspace] Hoberg, Rothvoss~\cite{HobergR17}
    & $\le \opt(I) + O(\log\opt(I))$
\\ \bottomrule
\end{tabular}
\label{table:offline-1bp}
\end{table}

On the hardness side, to the best of our knowledge,
an $\opt(I) + 1$ algorithm hasn't yet been proven to not exist.

\section{Geometric Bin Packing}

The Next-Fit Decreasing Height (NFDH) algorithm by
Coffman, Garey, Johnson and Tarjan~\cite{coffman1980performance}
is one of the simplest algorithms for 2D GBP
(for both the rotational and non-rotational versions),
which is 4-asymptotic-approximate.
Chung, Garey and Johnson~\cite{chung1982packing}
gave an algorithm for non-rotational 2D GBP, which we call FFDH-FF,
and proved that it has an AAR of $17/8 = 2.125$.
Kenyon and R\'emila~\cite{kenyon1996strip} gave an APTAS for
a problem called \emph{2D strip packing}, which gives a
$(2+\eps)$-asymptotic-approximation algorithm for non-rotational 2D GBP.

Caprara~\cite{caprara2008} gave an algorithm for $d$D GBP, called $\hdhk$,
that takes a parameter $k$ as input and has an AAR of roughly
$T_{\infty}^{d-1}$ (recall that $T_{\infty} \approx 1.69103$) when $k$ is large.
Caprara also simplified and improved the proofs of approximation of some known algorithms,
e.g., the AAR of FFDH-FF is $187/90 = 2.0\overline{7}8$.
Their results, along with those of Baker and Coffman~\cite{baker1981tight},
imply that the AAR of NFDH is $2T_{\infty} \approx 3.38206$.
All the results in~\cite{caprara2008} (including the $\hdhk$ algorithm)
only work for the non-rotational version.

Bansal, Caprara and Sviridenko gave an algorithm for 2D GBP,
for both the non-rotational version and the rotational version when the bin is square,
having an AAR of $1 + \ln(T_{\infty}) + \eps \approx 1.52534 + \eps$~\cite{rna}.
Their algorithm was a combination of the Round-and-Approx (R\&A) framework~\cite{rna}
and the HDH algorithm by Caprara~\cite{caprara2008}.
Jansen and Pr\"adel gave a $(1.5 + \eps)$-asymptotic-approximation
algorithm for 2D GBP~\cite{JansenP2013,jansen2016new}
for both the non-rotational version and the rotational version when the bin is square.
Bansal and Khan~\cite{bansal2014binpacking} combined Jansen and Pr\"adel's algorithm
with the Round-and-Approx framework to improve the AAR to
$1 + \ln 1.5 + \eps \approx 1.40547 + \eps$.

\begin{table}[ht]
\centering
\caption{Algorithms for 2D geometric bin packing.}
\begin{tabular}{lll}
\toprule Algorithm & Asymptotic Approximation Ratio & Works for rotational version?
\\ \midrule NFDH~\cite{coffman1980performance}
    & 4 & Yes
\\[\defaultaddspace] NFDH~\cite{coffman1980performance,caprara2008,baker1981tight}
    & $2T_{\infty} \approx 3.38206$ & No
\\[\defaultaddspace] FFDH-FF~\cite{coffman1980performance,caprara2008}
    & $187/90 \approx 2.0\overline{7}8$ & No
\\[\defaultaddspace] HDH~\cite{caprara2008}
    & $T_\infty \approx 1.69103$ & No
\\[\defaultaddspace] HDH with R\&A~\cite{rna}
    & $1 + \ln(T_\infty) + \eps \approx 1.52534 + \eps$
    & Yes (square bin only)
\\[\defaultaddspace] Jansen, Pr\"adel~\cite{JansenP2013,jansen2016new}
    & $1.5 + \eps$
    & Yes (square bin only)
\\[\defaultaddspace] Bansal, Khan~\cite{bansal2014binpacking}
    & $1 + \ln(1.5) + \eps \approx 1.40547 + \eps$
    & Yes (square bin only)
\\ \bottomrule
\end{tabular}
\label{table:2gbp}
\end{table}

Bansal, Correa, Kenyon and Sviridenko~\cite{bansal2006bin}
give an APTAS for $d$D BP for the case where all items are $d$D cubes
(recall that a cube is a cuboid having the same length in each dimension).

Bansal, Correa, Kenyon and Sviridenko~\cite{bansal2006bin}
proved that if P$\neq$NP, then an APTAS does not exist for 2D GBP.
Chleb{\'\i}k and Chleb{\'\i}kov\'a~\cite{chlebik2009hardness} proved that it is NP-hard to solve
2D GBP with an AAR better than $1+1/3792 \approx 1.000264$ for the non-rotational version
and an AAR better than $1+1/2196 \approx 1.000455$ for the rotational version.
Hence, unlike classical bin packing, an APTAS cannot exist for 2D GBP.

For the version of 3D GBP where items can be rotated about all axes,
Miyazawa and Wakabayashi~\cite{miyazawa2009three} gave a
4.89-asymptotic-approximation algorithm.
Epstein and van Stee~\cite{epstein2006side} improved the AAR to
4.5 when the base of the bin is a square.

\section{Geometric Knapsack}

In the $d$D geometric knapsack problem ($d$D GKS), we are given a set $I$ of items,
where each item $i \in I$ is a $d$D cuboid and has a profit $p(i) \ge 0$ associated with it.
Our goal is to pack the maximum profit subset of $I$ into a $d$D cuboidal bin.
In this problem, the bin is also called \emph{knapsack}.
We can have different versions of the problem depending on whether items
are allowed to be rotated or not.

%For both the rotational and the non-rotational version of the problem,
%a variant of Steinberg's algorithm gives a 3-approx algorithm.
Jansen and Zhang give a $(2+\eps)$-approximation algorithm~\cite{jansen2004rectangle}
for both the rotational and non-rotational versions of 2D GKS.
G\'alvez, Grandoni, Heydrich, Ingala, Khan and Wiese give a
$17/9 + \eps \approx 1.\overline{8}9 + \eps$ approximation algorithm
for non-rotational 2D GKS and a $(3/2 + \eps)$-approximation algorithm
for the rotational version when the knapsack is square.

For the special case of 2D GKS where $p(i)/a(i)$ is lower and upper bounded by constants
for each item $i \in I$, there is a PTAS to pack a maximum-profit subset of $I$
into a knapsack~\cite{bansal2009structural}. This works for both the
non-rotational and rotational version.

For 3D GKS, \cite{diedrich2008approximation} give a $(7+\eps)$-approximation
algorithm for the non-rotational version.
When items can be rotated by 90$^{\circ}$ either around the vertical axis only
or around all axes, they obtain algorithms with approximation ratios
$6 + \eps$ and $5 + \eps$, respectively, assuming that the knapsack is a cube.

\section{Strip Packing}

In the $d$D strip packing problem ($d$D SP),
we are given a set $I$ of $d$D cuboidal items.
Our goal is to pack the items into a single $d$D cuboid, called \emph{strip},
where the first $d-1$ dimensions of the strip are given
and the $d\Th$ dimension of the strip (called \emph{height}) must be minimized.
We get different versions of the problem depending on whether
items are allowed to be rotated or not.

For any $d$D cuboid, the first $d-1$ dimensions are called \emph{base dimensions},
and the $d\Th$ dimension is called the \emph{height}.
When item rotations are not allowed, we can assume \wLoG{} that
the strip has length 1 in each base dimension, and that the
maximum height of an item is at most 1.
This is because we can scale the dimensions of the bins and items by the same factor.

\begin{definition}[Asymptotic approximation for SP]
A strip packing algorithm $\Acal$ is said to be
$\alpha$-asymptotic-approximate iff for each input $I$,
$\Acal$ packs $I$ into a strip of height at most
$\alpha\opt(I) + \beta h_{\max}$
for some value $\beta \in o(\opt(I))$ (usually, $\beta$ is a constant),
where $h_{\max}$ is the maximum height of any item in $I$.
$\alpha$ is called the asymptotic approximation ratio (AAR) of $\Acal$.
\end{definition}
We can similarly define what it means for a strip packing algorithm to be an APTAS.

When all items in a $d$D SP instance have the same height,
and item rotations are not allowed, then the problem reduces to $(d-1)$D GBP.
Therefore, $d$D SP is a generalization of $(d-1)$D GBP.

Coffman, Garey, Johnson and Tarjan~\cite{coffman1980performance}
gave two algorithms for non-rotational 2D SP,
called Next-Fit Decreasing Height (NFDH) and First-Fit Decreasing Height (FFDH).
NFDH packs items into a strip of height less than $2\opt(I) + h_{\max}$,
where $h_{\max}$ is the maximum height of any item in the input.
FFDH packs items into a strip of height less than $1.7\opt(I) + h_{\max}$.
The approximation guarantee of NFDH also holds for the rotational version,
regardless of how we orient the items in the packing.
FFDH can be made to work for the rotational version with a bit more work.
% TODO: show how to make FFDH work for the rotational case.

Kenyon gave an APTAS for non-rotational 2D SP~\cite{kenyon1996strip}.
Jansen and van Stee gave an APTAS for rotation 2D SP~\cite{jansen2005strip},
under the assumptions that items have width and height at most 1
and that the strip has width equal to 1.

Caprara~\cite{caprara2008} gave an algorithm for the
non-rotational $d$D SP, called $\hdhk$,
that takes a parameter $k$ as input and has an AAR of roughly
$T_{\infty}^{d-1}$ for large $k$
(recall that $T_{\infty} \approx 1.69103$).

Li and Cheng~\cite{li1990three} give a 3.25-asymptotic-approximation
algorithm for non-rotational 3D SP.
Jansen and Solis-Oba~\cite{jansen2006asymptotic} improve the AAR to $2+\eps$.
Bansal, Han, Iwama, Sviridenko and Zhang~\cite{bansal2007harmonic}
improve the AAR to $T_{\infty} \approx 1.69103$.
Jansen and Pr\"adel~\cite{jansen2014new} further improve the AAR to $1.5 + \eps$.

Miyazawa and Wakabayashi~\cite{miyazawa2009three} gave a
2.64-asymptotic-approximation algorithm for 3D SP
when items can be rotated about all axes.
Epstein and van Stee~\cite{epstein2006side} give a
2.25-asymptotic-approximation algorithm for 3D SP
where the base of the strip is a square
and the items can be rotated either about all axes
or about the height axis only.

\section{Vector Bin Packing}

Lueker and Vega~\cite{bp-aptas} gave a $(d+\eps)$-asymptotic-approximation
algorithm for $d$D VBP.

Chekuri and Khanna~\cite{chekuri-khanna-vbp} showed that
if $d$ is not a constant, then for all $\eps > 0$, it is NP-hard to
obtain an algorithm for $d$D VBP having an AAR of $d^{1/2-\eps}$.
They showed this by reducing from the graph coloring problem.
Bansal, Khan and Elias~\cite{bansal2016improved}
show how to improve the hardness to $d^{1-\eps}$.
Due to these hardness results, we now focus only on the case where $d$ is a constant.

Chekuri and Khanna~\cite{chekuri-khanna-vbp} gave an algorithm for $d$D VBP
(for constant $d$) having an AAR of $2 + H_{d-1}$, where
$H_k \defeq 1 + 1/2 + \ldots + 1/k$ is the $k\Th$ harmonic number.
Using the well-known inequality $H_k \le \ln(k+1) + \gamma$,
% see https://math.stackexchange.com/a/306379
where $\gamma \approx 0.5772156649$ is the Euler–Mascheroni constant,
we get that the AAR is at most $2 + \gamma + \ln d$.

Bansal, Caprara and Sviridenko~\cite{rna} improved the AAR to
$1 + \ln d + \eps$ by combining the R\&A framework with Lueker and Vega's
$(d+\eps)$-asymptotic-approximation algorithm.

Bansal, Khan and Elias~\cite{bansal2016improved} gave an algorithm for 2D VBP
having an AAR of $1 + \ln(1.5) + \eps \approx 1.40547 + \eps$.
They also give an algorithm for $d$D VBP having an AAR of
$(1.5 - \ln 2) + \ln(d+1) + \eps$, which improves upon the previous
$(1 + \ln d + \eps)$-asymptotic-approximation algorithm~\cite{rna} when $d \ge 5$.
Their algorithms also use the R\&A framework.
They also give an algorithm having an absolute approximation ratio of $3/2 + \eps$,
which is tight (hardness of $3/2$ follows from classical bin packing).

\begin{table}[ht]
\centering
\caption{Algorithms for vector bin packing.}
\begin{tabular}{ll}
\toprule Algorithm & Asymptotic Approximation Ratio
\\ \midrule Lueker, Vega~\cite{bp-aptas}
    & $d+\eps$
\\[\defaultaddspace] Chekuri, Khanna~\cite{chekuri-khanna-vbp}
    & $2 + H_{d-1} \le 2.57722 + \ln d$
\\[\defaultaddspace] Bansal, Caprara, Sviridenko~\cite{rna}
    & $1 + \ln d + \eps$
\\[\defaultaddspace] Bansal, Khan and Elias~\cite{bansal2016improved}
    & $(1.5 - \ln 2) + \ln(d+1) + \eps \approx 0.80685 + \ln(d+1) + \eps$
\\[\defaultaddspace] Bansal, Khan and Elias~\cite{bansal2016improved}
    & $1 + \ln(1.5) + \eps \approx 1.40547 + \eps$\quad (for $d=2$)
\\ \bottomrule
\end{tabular}
\label{table:vbp}
\end{table}

Woeginger~\cite{woeginger1997there} proved that it is NP-hard to obtain an APTAS for 2D VBP.
Recently, Sandeep~\cite{sandeep2021optimal} showed that there exists a constant $c > 0$ such that
it is NP-hard to obtain an AAR less than $c\log d$ for $d$D VBP.

\section{Vector Knapsack}

In the $d$D vector knapsack problem ($d$D VKS), we are given a set $I$ of $d$D vectors,
where each vector has a non-negative profit associated with it,
and we have to pack a maximum-profit subset of $I$ into a single bin
(here the bin is also called \emph{knapsack}).

A PTAS for $d$D VKS was given by Frieze and Clarke~\cite{frieze1984approximation}.
