\section{Harmonic Algorithm for \texorpdfstring{$d$}{d}MCKS}
\label{sec:hdhks}

In the $d$D knapsack problem ($d$KS), we are given a set $I$ of $d$D items,
and a profit $p(i)$ for each item $i \in I$. We have to compute
a maximum-profit packing of a subset of $I$ (without rotating the items)
into a $d$D unit cube (called a knapsack).

In the $d$D multiple-choice knapsack problem ($d$MCKS),
we are given a set $\Ical = \{I_1, I_2, \ldots, I_n\}$ as input,
where for each $j$, $I_j$ is a set of items, called an {\em itemset},
and each item $i \in I_j$ has a profit $p(i)$.
We have to pick at most one item from each itemset and pack those items
into a $d$D bin such that the total profit is maximized.

For a $d$D item $i$, $\btype(i)$ (called \emph{base type}) is defined to be
a $(d-1)$-dimensional vector whose $j\Th$ component is $\type_k(\ell_j(i))$.
Define $\wfk(i)$ to be the cuboid $\itild$ where $\ell_j(\itild) \defeq f_k(\ell_j(i))$
for $j \in [d-1]$ and $\ell_d(\itild) \defeq \ell_d(i)$.
Define $\wfk(I) \defeq \{\wfk(i): i \in I\}$.
Similarly define $\wHk(i)$ and $\wHk(I)$.

We will see a fast and simple algorithm $\hdhknf(I)$ (\cref{algo:hdhknf}) for $d$BP
that we will use to design an algorithm for $d$MCKS.

\begin{algorithm}[!ht]
\caption{$\hdhknf(I)$:
Returns a bin packing of $d$D items $I$ ($d \ge 2$).}
\label{algo:hdhknf}
\begin{algorithmic}[1]
\State Let $P$ be the list of shelves output by $\hdhkspHyp(I)$.
\Comment{cf.~\cref{sec:hdhk-sp} for $\hdhksp$.}
\State Let $P'$ be an empty list.
\For{each $\btype$ $q$}
    \State Let $S_1^{[q]}, S_2^{[q]}, \ldots, S_{p^{[q]}}^{[q]}$
        be the shelves in $P$ of $\btype$ $q$, in decreasing order of height.
    \State Pack $S_1^{[q]}$ in a $d$D bin.
    \State For $j \ge 2$, add $S_j^{[q]}$ to $P'$.
\EndFor
\State Interpreting each shelf $S_j^{[q]}$ in $P'$ as a 1D item of size $\ell_d(S_j^{[q]})$,
    pack the shelves into $d$D bins using Next-Fit.
\end{algorithmic}
\end{algorithm}

Note that $\hdhknf(I)$ runs in $O(n\log n)$ time.

\begin{theorem}
\label{thm:hdhk-nf-fvol}
$\hdhknf(I)$ uses at most $Q + \smallceil{2\vol(\wfk(I))}$ bins,
where $Q$ is the number of distinct $\btype$s of items.
\end{theorem}
\begin{proof}
For each $q \in [Q]$, $S_1^{[q]}$ occupies one bin.

As per \cref{eqn:wfk-lb-height} in the proof of \cref{thm:hdhk-fvol},
for all $t \le p^{[q]}-1$, we get $\vol(\wfk(S_t^{[q]}))
%\ge \vol(f_k(S_t^{[q] (d-1)}))\ell_d(S_{t+1}^{[q]})
\ge \ell_d(S_{t+1}^{[q]})$.

Let $H$ be the total height of the shelves in $P'$. Then
\begin{align*}
H &= \sum_{q=1}^Q \sum_{t=1}^{p^{[q]}-1} \ell_d(S_{t+1}^{[q]})
\le \sum_{q=1}^Q \sum_{t=1}^{p^{[q]}-1} \vol(\wfk(S_t^{[q]}))  \tag{by \eqref{eqn:wfk-lb-height}}
\\ &< \sum_{q=1}^Q \sum_{t=1}^{p^{[q]}} \vol(\wfk(S_t^{[q]}))
= \vol(\wfk(I))
\end{align*}
Next-Fit guarantees that for a 1BP instance $J$,
number of bins used is at most $\ceil{2\vol(J)}$ (see \cref{thm:next-fit}).
So for the shelves in $P'$, we use $\ceil{2H}$ bins.
The total number of bins used is therefore
$Q + \ceil{2H} \le Q + \smallceil{2\vol(\wfk(I))}$.
\end{proof}

By \cref{thm:wfvol-sp,thm:hdhk-nf-fvol}, we get that $\hdhknf$ is $2T_k^{d-1}$-\asymAppx{}.

Lawler gave an FPTAS for 1MCKS that has a running time of
$O(N\log N + Nn/\eps)$~\cite{lawler1979fast},
where $N \defeq |\flatten(\Ical)|$ and $n \defeq |\Ical|$.
We will use it along with $\hdhknf[3]$ to get an algorithm for $d$MCKS,
called $\hdhks$ (see \cref{algo:hdhks}).

Our algorithm for $d$MCKS, called $\hdhks(\Ical)$, works as follows:
It computes a 1MCKS instance $\Icalhat$ by replacing each item $i$ in $\Ical$
by a 1D item $\vol(\wHk[3](i))$.
It uses the FPTAS for 1MCKS to obtain a $(1+\eps)$-\appx{} solution $J$ to $\Icalhat$.
It uses $\hdhknf[3]$ to pack the corresponding $d$D items of $J$ into bins.
It then selects the most profitable bin.
See \cref{algo:hdhks} for a more detailed description.

\begin{algorithm}[!ht]
\caption{$\hdhks(\Ical)$: algorithm for $d$MCKS.}
\label{algo:hdhks}
\begin{algorithmic}[1]
\State $\Icalhat = \{\{\vol(\wHk[3](i)): i \in I\}: I \in \Ical\}$.
\Comment{Reduction to 1MCKS.}
\State Let $\Jhat$ be a $(1+\eps)$-\appx{} solution to the 1MCKS instance $\Icalhat$
    output by the FPTAS for 1MCKS.
\State Let $J$ be the items of $\Ical$ corresponding to $\Jhat$.
\State Let $[J_1, J_2, \ldots, J_b]$ be the bin packing of $J$ produced using $\hdhknf[3]$.
\State ${\displaystyle j_{\max} = \argmax_{j=1}^b p(J_j)}$
\State \Return $J_{j_{\max}}$.
\end{algorithmic}
\end{algorithm}

$\hdhks$ runs in $O(N\log N + Nn/\eps)$ time.

\begin{theorem}
\label{thm:emb-ks}
$\hdhks$ is $3^d(1+\eps)$-\appx{}.
\end{theorem}
\begin{proof}
Let $I$ be a set of $d$D items.
Suppose $S \subseteq I$ can be packed into a bin.
Then by \cref{thm:dff-pack}, $\widehat{S} = \{\vol(\wHk[3](i)): i \in S\}$
can also be packed into a bin. Therefore, $\optdmcks[1](\Icalhat) \ge \optdmcks(\Ical)$.

The FPTAS for 1MCKS gives us $\Jhat$ such that
$p(\Jhat) \ge \optdmcks[1](\Icalhat)/(1+\eps)$.
$\hdhknf$ packs $J$ into
$b \le 3^{d-1} + \smallceil{2T_3^{d-1}\vol(\wHk[3](J))} \le 3^d$ bins.
Given the way we choose $j_{\max}$,
\[ p(J_{j_{\max}}) \ge \frac{p(J)}{b} = \frac{p(\Jhat)}{b}
\ge \frac{\optdmcks[1](\Icalhat)}{b(1+\eps)} \ge \frac{\optdmcks(\Ical)}{3^d(1+\eps)}  \qedhere \]
\end{proof}
